---
title: "Dashboard Reserve Management"
date: "`r format(Sys.Date(), '%b-%Y')`"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
    css: www/styles1.css
    source_code: embed
    logo: www/eccb4.png
    social: [menu]
    navbar:
        - { icon: "fa-github", href:"https://github.com/ahodge", align: right }
        - { icon: "fa-linkedin", href: "https://www.linkedin.com/in/eastern-caribbean-central-bank/", align: right }
        - { icon: "fa-at", href: "mailto:allister.hodge@eccb-centralbank.org", align: right }
---
pppp

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
# sys.source("packages/load_packages.R", envir = knitr::knit_global())
# source('packages/load_packages.R',local = knitr::knit_global())
# Install thematic and un-comment for themed static plots (i.e., ggplot2)
# thematic::thematic_rmd()
read_chunk('packages/load_packages.R')
library(pacman)
require(tidyverse)
require(data.table)
require(here)
library(tools)
library(metathis)
library(r2social)
library(fontawesome)
suppressPackageStartupMessages(pacman::p_load(scales, glue, fs, lubridate,
                                              highcharter, plotly,
TSstudio,dygraphs,downloadthis, tbl2xts,reactable,reactablefmtr,DT, gt, 
gtExtras, readxl,tsibble, fable, fabletools,ragg,
fable.ata, fable.prophet,ggsci, ggrepel,tbl2xts))


library(fredr)
fredr::fredr_set_key('7d33f9e550f6a2a4a8161e0207f497b3')

knitr::opts_chunk$set(echo = FALSE, 
                      collapse = TRUE,
                      comment = "#>",
                      fig.path = "./graphs",
                      fig.retina = 2, # Control using dpi
                      fig.width = 6,  # generated images
                      fig.pos = "t",  # pdf mode
                      fig.align = "center",
                      dpi = if (knitr::is_latex_output()) 72 else 300, 
                      out.width = "100%",
                      dev = "ragg_png",
                      dev.args = list(png = list(type = "cairo-png")),
                      optipng = "-o1 -quiet")
                                              
```

Row
-------------------

### Conditional Value at Risk/Expected Shortfall
```{r cvar}

htmltools::includeMarkdown('www/cvar.md')
```


### Duration Risk
Duration is a measure of price sensitivity of bonds to interest rate changes.The longer the duration or maturity of a bond, the more sensitive is its price to a change in interest rates.

There are 4 types of duration considered in the literature:
1. Effective Duration
2. Modified Duration 
3. Macaulay Duration
4. Key Rate Duration

**To set ideas below is an example of how to interpret duration:** 

1) If modified duration is 1 (year) and interest rate change is +25bp (= +0.25%), % change of bond price is equal to -0.25% (= -1*0.25%).

2) If modified duration is 10 (years) and interest rates change by +25bp (= +0.25%), % change of bond price is equal to -2.5% (= -10*0.25%).

* As at `r format(Sys.Date(), '%b-%Y')` **Macaulay Duration** for the reserve portfolio was 1.88.   
* As at `r format(Sys.Date(), '%b-%Y')` **Modified Duration** of the reserve portfolio was 1.41.


**Convexity**
*Convexity is a measure of the curvature of the relationship between the price of a bond and its yield. It provides an additional refinement to duration as a measure of a bond’s sensitivity to interest rate changes.*

* Convexity is typically expressed in terms of percentage, and it represents the relative change the price of bond  for a given change in yield.
* Effective convexity takes into account the modified duration and the change in yield, providing a more accurate measure of a bonds price sensitivity to interest rate changes.
* Effective convexity provides a more precise estimate of the bond price change compared to convexity, especially when the yield changes are significant.

Row
------------
### Stop Loss Model

```{r gauge_plot, echo=FALSE}
col_stops <- data.frame(
  q = c(0.15, 0.4, .8),
  c = c('#55BF3B', '#DDDF0D', '#DF5353'),
  stringsAsFactors = FALSE)

highchart() %>%
  hc_chart(type = "solidgauge") %>%
  hc_pane(
    startAngle = -90,
    endAngle = 90,
    background = list(
      outerRadius = '100%',
      innerRadius = '60%',
      shape = "arc")
  ) %>%
  hc_tooltip(enabled = FALSE) %>% 
  hc_yAxis(
    stops = list_parse2(col_stops),
    lineWidth = 0,
    minorTickWidth = 0,
    tickAmount = 2,
    min = 0,
    max = 100,
    labels = list(y = 26, style = list(fontSize = "22px"))
  ) %>%
  hc_add_series(
    data = 90,
    dataLabels = list(
      y = -50,
      borderWidth = 0,
      useHTML = TRUE,
      style = list(fontSize = "40px")
    )
  ) %>% 
  hc_size(height = 300)



```

Row
--------
### Heat-map Stop Loss Model
```{r stop loss2}
set.seed(123)
m <- matrix(round(rnorm(200), 2), 12, 12)

colnames(m) <- month.name
# colnames(m) <- paste("Col", 1:10)
rownames(m) <- paste(2023:2012 )

as_tibble(m) %>% 
  mutate(year = as.character(2012:2023)) %>% 
  relocate(year, .before = January) %>% 
  gt() %>% 
  tab_style_body(
    columns = c(2:13),
    style = cell_fill(color = "green"),
    fn = \(x) x<0
    ) %>% 
  tab_style_body(
    columns = c(2:13),
    style = cell_fill(color = "orange"),
    fn = \(x) x>=0 && x<=1.5) %>% 
 
  tab_style_body(
    columns = c(2:13),
    style = cell_fill(color = "red"),
    fn = function(x) x >= 1.51) %>% 
  tab_footnote(
    'Data here is stylised meant to show a graphical\nrepresentation of a heatmap for the stop loss',
    locations =  cells_column_labels(columns = January),
    placement = c("left")
  )

```


Row 
-------------------------------------------------------------------------------
### GDP OECD

```{r OECD_GDP, echo=FALSE, warning=FALSE, fig.width=4}
df <- read_csv('data/gdp_oecd.csv ')


df2 <- df %>%  select(c(1,5,9,17)) %>% 
  dplyr::rename_all(~tolower(.)) %>% 
  mutate(time = ym(time)) |>
  filter(measure == 'GYSA') %>% 
  pivot_wider(names_from = location, values_from = value) %>% 
  mutate_if(is.numeric, ~round(.,2))


p_gdp <- df2[,c(2:7)] %>%  
  # filter(time >= as.Date('2021-01-01')) %>% 
  
  pivot_longer(names_to = 'Country', values_to = 'value', -time)


  hchart(p_gdp, "line", hcaes(x = time, y = value, 
                               group = Country)) |>
  hc_title(text= "GDP OECD Countries incl China") |> 
  hc_caption(text = "Data Source | St Louis Fred" ) |>
   hc_yAxis(
    title = list(text = "Percent Change (%)")) |>
  hc_plotOptions(
    line = list(lineWidth = 5)) |>
  hc_rangeSelector(enabled = F)
  

```

Row
-----------
### Unemployment Rates OECD
```{r labour_oecd, echo=FALSE}
path <- "data/labour_oecd.xlsx"


df <- path %>%  
  excel_sheets() %>% 
  purrr::set_names() %>% 
  map(read_excel, path = path)


df <- read_csv('data/labour_oecd.csv ')


df2 <- df %>%  select(c(1,9,17)) %>% 
  dplyr::rename_all(~tolower(.)) %>% 
  mutate(time = ym(time)) %>% 
  pivot_wider(names_from = location, values_from = value) %>% 
  mutate_if(is.numeric, ~round(.,2)) %>% 
  dplyr::rename(date = time)



p_unemployment <- tbl2xts::tbl_xts(df2 )
 




highchart(type = "stock") %>% 
  hc_add_series(p_unemployment$CAN, type = "line",
                name = 'CAN',
                color = "#d35400",
                tooltip = list(valueSuffix = '%')) %>% 
  
  hc_add_series(p_unemployment$USA, type = "line",
                name = 'USA',
                tooltip = list(valueSuffix = '%')) %>% 
  hc_add_series(p_unemployment$GBR, type = "line",
                name = 'UK',
                tooltip = list(valueSuffix = '%')) %>%
  hc_add_series(p_unemployment$EA20, type = "line",
                name = 'Euro-Area',
                tooltip = list(valueSuffix = '%')) %>%
  
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y')),
                     buttonTheme = list(
                       fill =  'none',
                       stroke = 'none',
                       style = list(
                         color = '#039',
                         fontWeight = 'bold')),
                   inputBoxBorderColor = 'gray',
                   inputBoxWidth = 120,
                   inputBoxHeight = 18,
                   inputStyle = list(
                     color = '#039',
                     fontWeight =  'bold')
                     ) %>% 
  
  hc_title(text = 'Unemployment Rates OECD', align = 'center') |>
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = 
             list(style = list(
               color = 'black',
               fontSize = 'medium')),
           dateTimeLabelFormats = list(day = '%Y'), type = "datetime") |>
  hc_legend(
    enabled = TRUE,
    align = "left",
    verticalAlign = "top",
    layout = "horizantal") |>
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "Unemployment Rates OECD") |>                      

  hc_tooltip(shared = FALSE)

 
 
# fig1 <- plot_ly(p_unemployment, x = ~time) 

# fig1 %>% 
#   add_lines(y = ~`value`, name = "Unemployment Rate") %>% 
  # add_lines(y = ~`two-year`, name = "Two-year") %>% 
  # add_lines(y = ~`fed-funds`, name = "Fed-Funds") %>% 
  # add_lines(y = ~`six-months`, name = "Six-Months") %>% 
  # add_lines(y = ~`three-month`, name = "Three-Months")

```


### Inflation Rates OECD
```{r inflation_oecd}
df <- read_csv('data/cpi_oecd.csv ')



df2 <- df %>%  select(c(1,3,9,17)) %>% 
  dplyr::rename_all(~tolower(.)) %>% 
  mutate(time = ym(time)) %>% 
  filter(subject == 'CPALTT01') %>% 
  pivot_wider(names_from = location, values_from = value) %>% 
  mutate_if(is.numeric, ~round(.,2))


p_cpi_oecd <- df2[,c(2:6)] %>% 
  dplyr::rename(date = time)



p_cpi_oecd_xts <- tbl2xts::tbl_xts(p_cpi_oecd)


highchart(type = "stock") %>% 
  hc_add_series(p_cpi_oecd_xts$CAN, type = "line",
                name = 'CAN',
                color = "#EE160C",
                tooltip = list(valueSuffix = '%')) %>% 
  
  hc_add_series(p_cpi_oecd_xts$USA, type = "line",
                name = 'USA',color = '#020817',
                tooltip = list(valueSuffix = '%')) %>% 
  hc_add_series(p_cpi_oecd_xts$GBR, type = "line",
                name = 'UK',
                color = '#0C4AEE',
                tooltip = list(valueSuffix = '%')) %>%
  hc_add_series(p_cpi_oecd_xts$EA20, type = "line",
                name = 'Euro-Area',
                color = '#04A532',
                tooltip = list(valueSuffix = '%')) %>%
  
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y')),
                     buttonTheme = list(
                       fill =  'none',
                       stroke = 'none',
                       style = list(
                         color = '#039',
                         fontWeight = 'bold')),
                   inputBoxBorderColor = 'gray',
                   inputBoxWidth = 120,
                   inputBoxHeight = 18,
                   inputStyle = list(
                     color = '#039',
                     fontWeight =  'bold')
                     ) %>% 
  
  hc_title(text = 'Inflation Rates OECD', align = 'center') |>
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = 
             list(style = list(
               color = 'black',
               fontSize = 'medium')),
           dateTimeLabelFormats = list(day = '%Y'), type = "datetime") |>
  hc_legend(
    enabled = TRUE,
    align = "left",
    verticalAlign = "top",
    layout = "horizantal") |>
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "Inflation Rates OECD") |>                      

  hc_tooltip(shared = FALSE)

```


Row 
-------------------------------------------------------------------------------
### Real GDP Growth 
```{r gdp_gRowth, echo=FALSE,warning=FALSE,fig.width=4}
gdp <- fredr(
  series_id = "GDPC1",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  units = 'cca')

gdp1 <- gdp %>% dplyr::select(c(date, value)) 



p_gdp <- tbl2xts::tbl_xts(gdp1 )
 




highchart(type = "stock") %>% 
  hc_add_series(p_gdp$value, type = "line",
                name = 'GDP-USA',
                color = "#d35400",
                tooltip = list(valueSuffix = '%')) %>% 
  
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y')),
                     buttonTheme = list(
                       fill =  'none',
                       stroke = 'none',
                       style = list(
                         color = '#039',
                         fontWeight = 'bold')),
                   inputBoxBorderColor = 'gray',
                   inputBoxWidth = 120,
                   inputBoxHeight = 18,
                   inputStyle = list(
                     color = '#039',
                     fontWeight =  'bold')
                     ) %>% 
  
  hc_title(text = '<b>Real GDP Growth USA</b>', align = 'center',
           useHTML = TRUE) |>
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = 
             list(style = list(
               color = 'black',
               fontSize = 'medium')),
           dateTimeLabelFormats = list(day = '%Y'), type = "datetime") |>
  hc_legend(
    enabled = TRUE,
    align = "left",
    verticalAlign = "top",
    layout = "horizantal") |>
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "GDP USA") |>                      

  hc_tooltip(shared = FALSE)


```


### GDP Nowcast
```{r gdp_nowcast, echo = FALSE}
gdpnow <- fredr(
  series_id = "GDPNOW",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date())


gdpnow1 <- gdpnow %>% dplyr::select(c(date, value)) %>% 
  mutate(value = value/100)



p_gdpnow <- gdp %>%  
  dplyr::select(c('date', 'value')) %>% 
  left_join(dplyr::select(gdpnow,c('date', 'value')), by = 'date') |>
  setNames(c('date', 'GDP', 'GDP_now')) %>% 
  pivot_longer(names_to = 'GDP', values_to = 'values', -date) |>
   arrange(GDP) %>% 
   filter(date >= as.Date("2008-01-01")) |>
  ggplot(aes(x= date, y = values/100, color = GDP)) +
  geom_hline(yintercept = 0, linewidth = 1.2) +
  geom_line(linewidth = 1.2, lineend = 'round', na.rm = T) +
  scale_y_continuous(labels = scales::percent_format() ,
                     breaks = scales::breaks_width(0.05)) +
  scale_x_date(labels = scales::label_date("%Y"),
               date_breaks = '3 years') +
  scale_color_manual(values = c('black', 'red')) +
  labs(x= "Quarterly", y = 'GDP Growth', 
       caption = 'Source: St.Louis Fred\nData as at:',
       title = 'Real GDP Growth') +
  theme_minimal()

ggplotly(p_gdpnow)
```

Row
----------------------------------------------------------------------------
### Chicago Fed National Activity Index (CFNAI)
```{r CFNAI, echo=FALSE}
# Chicago Fed National Activity Index: Three Month Moving Average (CFNAIMA3)
gdp_cfnai <- fredr(
  series_id = "CFNAIMA3",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'q')

p_cfnai <- gdp_cfnai %>%  
  dplyr::select(c("date", "value"))

p_cfnai1 <- tbl2xts::tbl_xts(p_cfnai )
 


highchart(type = "stock") %>% 
  hc_add_series(p_cfnai1$value, type = "line",
                name = 'CFNAI',
                color = "#d35400",
                tooltip = list(valueSuffix = '%')) %>% 
  
 
  
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y')),
                     buttonTheme = list(
                       fill =  'none',
                       stroke = 'none',
                       style = list(
                         color = '#039',
                         fontWeight = 'bold')),
                   inputBoxBorderColor = 'gray',
                   inputBoxWidth = 120,
                   inputBoxHeight = 18,
                   inputStyle = list(
                     color = '#039',
                     fontWeight =  'bold')
                     ) %>% 
  
  hc_title(text = '<b>Chicago Fed National Activity Index</b>', align = 'center',
           useHTML = TRUE) |>
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = 
             list(style = list(
               color = 'black',
               fontSize = 'medium')),
           dateTimeLabelFormats = list(day = '%Y'), type = "datetime") |>
  hc_legend(
    enabled = TRUE,
    align = "left",
    verticalAlign = "top",
    layout = "horizantal") |>
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "CFNAI") |>                      

  hc_tooltip(shared = FALSE)

```



### Weekly Economic Index (WEI)
```{r WEI, echo=FALSE, warning=TRUE}
# Weekly Economic Index (Lewis-Mertens-Stock) (WEI)
gdpwei <- fredr(
  series_id = "WEI",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(), frequency = 'm')


p_gdpwei <- gdpwei %>%  
  dplyr::select(c("date", "value")) 



highchart(type = "stock") %>% 
  hc_add_series(data = p_gdpwei, type = "line", hcaes(x = date, y = value),
                name = "WEI", color = 'black',
                lineWidth = 4.5) |>
  
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
                        color = 'black',
                        fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) %>% 
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_title(text = "Weekly Economic Index", 
           style = list(fontWeight = 'bold')) |>
  hc_subtitle(
    text = "Weekly data aggregated to monthly using averages",
    style = list(color = "black", fontWeight = "bold")
  )  |>
  hc_legend(
    enabled = TRUE, 
    align = "right",
    verticalAlign = "top",
    layout = "vertical",
    verticalAlign=  'top')

```



Row
---------------------------------------------------------
### Inflation Rates USA
```{r cpi,echo=FALSE,warning=FALSE,fig.width=4}
cpi <- fredr(
  series_id = "CPIAUCSL",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  units = 'pc1')


cpi_core <- fredr(
  series_id = "CPILFESL",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  units = 'pc1')

# Inflation expectations data 1 year ahead only

inflation_exp <- fredr(
  series_id = "EXPINF1YR",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date())


cpi_join <- cpi %>%  
  dplyr::select(c('date', 'value')) %>% 
  left_join(dplyr::select(cpi_core, c('date', 'value')), by = 'date') %>% 
  mutate(across(where(is.numeric), ~round(.,2))) %>% 
  setNames(c("Date", 'CPI', 'cpicore')) %>% 
  pivot_longer(names_to = 'Inflation' , values_to = 'values',-Date)


# hchart(cpi_join, "line", hcaes(x = Date, y = values, 
#                                group = Inflation)) |>
#   hc_title(text= "Inflation Rates USA") |> 
#   hc_caption(text = "Data Source | St Louis Fred" ) |>
#    hc_yAxis(
#     title = list(text = "Percent Change (%)")) |>
#   hc_plotOptions(
#     line = list(lineWidth = 5)) |>
#        
#  hc_rangeSelector(verticalAlign = "bottom",  buttonPosition = 'left',
#   buttons = list(
#     list(type = 'all', text = 'All'),
#     list(type = 'ytd', text = 'YTD'),
#     list(type = 'month', count = 6, text = '6m'),
#     list(type = 'year', count = 1, text = '1y'),
#     list(type = 'year', count = 5, text = '5y'),
#     list(type = 'year', count = 10, text = '10y')))


pce <- fredr(
  series_id = "PCE",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  units = 'pc1')


pce_core <- fredr(
  series_id = "PCEPILFE",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  units = 'pc1')


pce_join <- pce %>%  
  dplyr::select(c('date', 'value')) %>% 
  left_join(dplyr::select(pce_core, c('date', 'value')), by = 'date') %>% 
  mutate(across(where(is.numeric), ~round(.,2))) %>% 
  setNames(c("Date", 'pce', 'pcecore'))


cpi2 <- cpi %>%  
  dplyr::select(c('date', 'value')) %>% 
  left_join(dplyr::select(cpi_core, c('date', 'value')), by = 'date') %>% 
  mutate(across(where(is.numeric), ~round(.,2))) %>% 
  setNames(c("Date", 'CPI', 'cpicore')) 
  
  
cpi_join1 <-cpi2 %>% 
  left_join(pce_join, by = 'Date' )
                         


cpi_join2 <- tbl2xts::tbl_xts(cpi_join1)

highchart(type = "stock") %>% 
  hc_add_series(cpi_join2$CPI, type = "line",
                name = 'CPI',
                color = "#d35400",
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '%')) %>% 

  hc_add_series(cpi_join2$cpicore, type = "line",
                name = 'CPI-Core',
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '%')) %>% 
  hc_add_series(cpi_join2$pce, type = "line",
                name = 'PCE',
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '%')) %>%
  hc_add_series(cpi_join2$pcecore, type = "line",
                name = 'PCE-Core',
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '%')) %>%
  
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) %>% 
  # hc_xAxis(dateTimeLabelFormats = list(day = '%Y'), type = "datetime") %>% 
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "Inflation Rates USA") |>                      
  hc_yAxis(labels = list(align = 'left',
                         
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
   hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
             color = 'black',
             fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_legend(enabled = TRUE)  |>
  # hc_legend(
  #   align = "top",
  #   verticalAlign = "top",
  #   layout = "horizantal") |>
  hc_tooltip(shared = FALSE) |>
 hc_title(
    text = "<b>Rates of Inflation USA</b>",
    margin = 20,
    align = "left",
    style = list(color = "black", useHTML = TRUE)
    )


```


### Trimmed Mean Inflation Measures
```{r trimmed_inflation,echo=FALSE,warning=FALSE,fig.width=4}
# Trimmed Mean PCE Inflation Rate Dallas Fed
inflation_exp2 <- fredr(
  series_id = "PCETRIM12M159SFRBDAL",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date())


# 16% Trimmed-Mean Consumer Price Index Cleveland Fed
inflation_exp3 <- fredr(
  series_id = "TRMMEANCPIM159SFRBCLE",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date())


# Median Consumer Price Index
inflation_exp4 <- fredr(
  series_id = "MEDCPIM159SFRBCLE",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date())

# sticky price inflation

inflation_exp1 <- fredr(
  series_id = "CORESTICKM159SFRBATL",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date())


cpi_alt <- inflation_exp2 %>% 
  dplyr::select(c('date', 'value')) %>% 
  left_join(dplyr::select(inflation_exp3,c('date', 'value')), by = 'date') |>
  left_join(dplyr::select(inflation_exp4,c('date', 'value')), by = 'date')  |>
  left_join(dplyr::select(inflation_exp1,c('date', 'value')), by = 'date')  |>
  setNames(c('date', 'Trimmed-Mean-PCE', '16%-Trimmed-Mean-CPI', 
             'Median-CPI','Sticky.Price.inflation')) %>% 
  dplyr::rename_all(~toTitleCase(.)) %>% 
  mutate(across(where(is.numeric), ~round(.,2)))


cpi_alt2 <- tbl2xts::tbl_xts(cpi_alt)

highchart(type = "stock") %>% 
  hc_add_series(cpi_alt2$Sticky.Price.inflation, type = "line",
                name = 'Sticky.Price.inflation',
                color = "#d35400",
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '%')) %>% 
  
  hc_add_series(cpi_alt2$`Trimmed-Mean-PCE`, type = "line",
                name = 'Trimmed-Mean-PCE',
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '%')) %>% 
  hc_add_series(cpi_alt2$`16%-Trimmed-Mean-CPI`, type = "line",
                name = '16%-Trimmed-Mean-CPI',
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '%')) %>%
  hc_add_series(cpi_alt2$`Median-CPI`, type = "line",
                name = 'Median-CPI',
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '%')) %>%
  hc_xAxis(dateTimeLabelFormats = list(year = '%Y'), type = "datetime") |>
  
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) |>
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "Inflation Rates USA"
  ) |>                      
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
             color = 'black',
             fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_legend(enabled = TRUE)  |>
  # hc_legend(
  #   align = "top",
  #   verticalAlign = "top",
  #   layout = "horizantal") |>
  hc_tooltip(shared = FALSE) |>
  hc_title(
    text = "<b>Rates of Inflation USA</b>",
    margin = 20,
    align = "left",
    style = list(color = "black", useHTML = TRUE)
  )

```


Row
-----------------------------------------------------------------------
### Oil Prices
```{r oil_prices,echo=FALSE,warning=FALSE,fig.width=4}
brent <- fredr(
  series_id = "DCOILBRENTEU",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')

wti <- gdp <- fredr(
  series_id = "DCOILWTICO",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')



oil <- brent[,c(1,3)] %>% left_join(wti, by = 'date') %>% 
  dplyr::select(c('date', 'value.x', 'value.y')) %>% 
  set_names(c('date', 'brent', 'wti')) %>% 
  pivot_longer(names_to = 'variable', values_to = 'value',
               -date)


hchart(oil, "line", hcaes(x = date, y = value, group = variable))
```


### Commodity Price Index 
```{r}
all_index <- fredr(
  series_id = "PALLFNFINDEXQ",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'q')

energy_index <- gdp <- fredr(
  series_id = "PNRGINDEXM",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'q')

food_index <- gdp <- fredr(
  series_id = "PFOODINDEXM",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'q')


nonenergy_index <- gdp <- fredr(
  series_id = "PNFUELINDEXM",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'q')


comm_index <- all_index %>% 
  select(c(date, value)) %>% 
  left_join(select(energy_index, c('date', 'value')), by = 'date') %>% 
  left_join(select(food_index, c('date', 'value')), by = 'date') %>%
  left_join(select(nonenergy_index, c('date', 'value')), by = 'date') %>%
  setNames(c('date', 'All', 'Energy',
             'Food', 'Non-Energy')) %>% 
  mutate(across(where(is.numeric), ~round(.,2)))
  


comm_index1 <- tbl2xts::tbl_xts(comm_index)
highchart(type = "stock") %>% 
  hc_add_series(comm_index1$Energy, type = "line",
                name = 'Energy Price Index',
                color = "#d35400",
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '')) %>% 
  
  hc_add_series(comm_index1$Food, type = "line",
                name = 'Food Price Index',
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '')) %>% 
  hc_add_series(comm_index1$`Non-Energy`, type = "line",
                name = 'Non Energy Price Index',
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '')) %>%
  
  hc_xAxis(dateTimeLabelFormats = list(year = '%Y'), type = "datetime") |>
  
  hc_rangeSelector(verticalAlign = "bottom",
                   buttonTheme = list(
                     fill= 'none',
                     stroke= 'none',
                     'stroke-width'= 0,
                     r= 8,
                     
                     style= list(
                       color= '#039',
                       fontWeight= 'bold'
                     )),
  
inputBoxBorderColor= 'gray',
inputBoxWidth= 120,
inputBoxHeight= 18,
inputStyle= list(
  color= '#039',
  fontWeight= 'bold'),
labelStyle= list(
  color= 'silver',
  fontWeight= 'bold')
) |>
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "Global Commodity Price Index"
  ) |>                      
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
             color = 'black',
             fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_legend(enabled = TRUE)  |>
  # hc_legend(
  #   align = "top",
  #   verticalAlign = "top",
  #   layout = "horizantal") |>
  hc_tooltip(shared = FALSE) |>
  hc_title(
    text = "<b>Global Commodity Price Index</b>",
    margin = 20,
    align = "left",
    style = list(color = "black", useHTML = TRUE)
  ) |>
  hc_subtitle(
    text = "Index 2016 = 100",
    align = "left",
    style = list(color = "black", fontWeight = "bold")
  ) 


```


Row {data-width= 700}
--------------------------------------------------------------------------------
### Unemployment Rate

```{r unemploy_rates, echo=FALSE,warning=FALSE,fig.width=4}
unrate <- fredr(
  series_id = "UNRATE",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date())


unrate1 <- unrate |>
dplyr::select(c('date', 'value'))

highchart(type = "stock") %>% 
  hc_rangeSelector(verticalAlign = "bottom", 
                   buttonTheme = list(
                     fill = "#505053",
                     stroke = "#000000",
                     style = list(color = "#CCC"),
                     states = list(
                       hover = list(
                         fill = "#707073",
                         stroke = "#000000",
                         style = list(color = "white")
                       ))),
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y')),
                   inputBoxBorderColor = 'gray',
                   inputBoxWidth = 120,
                   inputBoxHeight = 20) %>% 
  hc_add_series(unrate1, "line", color = "#337F05",
                tooltip = list(valueSuffix = '%'),
                hcaes(x = date, y = value)) %>% 
  hc_plotOptions(
    line = list(lineWidth = 5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "Unemployment rate"
  ) %>% 
  hc_title(text = 'USA Unemployment Rate', align = 'left') %>% 
  hc_yAxis(labels = list(align = 'left',
    
    style = list(
    color = 'black',
    fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = 
             list(style = list(
                  color = 'black',
                  fontSize = 'medium')))

```



### Unemployment Claims

```{r claims,echo=FALSE,warning=FALSE,fig.width=4}
# Initial Claims  (ICSA)
unemp_claims <- fredr(
  series_id = "ICSA",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  aggregation_method = 'avg',
  frequency = 'm',
  units = 'lin')

unemp_claims1 <- unemp_claims |>
  dplyr::select(c('date', 'value'))
#  plot_ly( x = ~date, y = ~value, type = 'scatter', mode = 'lines',
#           line = list(color = 'rgb(22, 96, 167)', width = 5)) |>
#   layout(title = "Unemployment Claims USA",
#          xaxis = list(title = "Months"),
#          yaxis = list (title = "Unemployment Claims Thousands"))


highchart(type = "stock") %>% 
  hc_add_series(data = unemp_claims1, type = "line", hcaes(x = date, y = value),
                name = "Unemployment Claims", color = 'black',
                lineWidth = 4.5) |>
  
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
                        color = 'black',
                        fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) %>% 
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_legend(
    enabled = TRUE, 
    align = "top",
    verticalAlign = "top",
    layout = "vertical",
    verticalAlign=  'top') |>
  hc_title(
    text = "<b>Unemployment Claims</b>",
    margin = 20,
    align = "center",
    style = list(color = "black", useHTML = TRUE)
    )

```


Row
--------------------------------------------------------------------------------
### Interest Rates 
```{r interest_rates,echo=FALSE,warning=FALSE,fig.width=4}

twoyear <- fredr(
  series_id = "DGS2",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')



oneyear <- fredr(
  series_id = "DGS1",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')

threemonth <- fredr(
  series_id = "DGS3MO",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')

sixmonth <- fredr(
  series_id = "DGS6MO",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


tbills <- fredr(
  series_id = "TB3MS",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


fedfunds <- fredr(
  series_id = "FEDFUNDS",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


irates <- cbind(threemonth[,c(1,3)],sixmonth[,3],
                oneyear[,3],
                twoyear[,3])
# fedfunds[,3]

names(irates) <- c('date','three-month', 'six-months',
                   'one-year',
                   'two-year')

irates1 <- irates %>%  
  left_join(dplyr::select(fedfunds, c('date', 'value')), by = 'date') %>% 
  dplyr::rename(`fed-funds` = value) %>% 
  modify_if(is.numeric,~./100) %>% 
  pivot_longer(names_to = 'rate_type', 
               values_to = 'interest_rate', 
               -date)


# p_rates_usa <- irates1 %>% 
#   filter(date>= as.Date('2008-01-01')) %>% 
#   ggplot(aes(x= date, y = interest_rate,color = rate_type)) +
#   geom_line(lineend = 'round', linewidth = 1.3, na.rm = T) +
#   scale_y_continuous(labels = scales::percent_format() ,
#                      breaks = scales::breaks_width(.005)) +
#   scale_x_date(labels = scales::label_date("%m-%Y"),
#                date_breaks = '12 months') +
#   labs(x= "Date", y = 'Interest rates', 
#        caption = 'Source: St.Louis Fred\nData as at:',
#        title = 'Key Benchmark Interest Rates') +
#   scale_color_jco() +
#   theme_minimal()
# #'
# #'
# #'
# 
# p_rates_usa %>%  
#   ggplotly()


irates2 <- irates1 |> 
  pivot_wider(names_from = rate_type, values_from = interest_rate) %>% 
  modify_if(is.numeric, ~.*100)




# hchart(irates1, "line", hcaes(x = date, y = interest_rate, 
#                               group = rate_type))
#  

highchart(type = "stock") %>% 
  hc_add_series(data = irates2, type = "line",
                hcaes(x = date, y = `fed-funds`),
                name = "Fed-Funds", color = "#8C2981",
                lineWidth = 4.5) |>
  hc_add_series(data = irates2, type = "line",
                hcaes(x = date, y = `one-year`),
                name = "One-Year", color = 'black',
                lineWidth = 4.5) |>
  hc_add_series(data = irates2, type = "line",
                hcaes(x = date, y = `two-year`),
                name = "Two-Year", color = 'red',
                lineWidth = 4.5) |>
  
  hc_add_series(data = irates2, type = "line",
                hcaes(x = date, y = `six-months`),
                name = "Six-Month", color = "#f1c40f",
                lineWidth = 4.5) |>
  hc_add_series(data = irates2, type = "line",
                hcaes(x = date, y = `three-month`),
                name = "Tnree-Month", color = "#2ecc71",
                lineWidth = 4.5) |>
  
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
             color = 'black',
             fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) %>% 
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_title(text = 'Interest rates USA',
           align = 'left',
           style = list(fontWeight = 'bold')) |>
  hc_legend(
    enabled = TRUE, 
    align = "top",
    verticalAlign = "top",
    layout = "vertical",
    verticalAlign=  'top')
 


```

### Yield Spreads
```{r yield-spreads, echo=FALSE,warning=FALSE,fig.width=4}


# 10-Year Treasury Constant Maturity Minus 2-Year Treasury Constant Maturity  (T10Y2Y)
yield_curve1 <- fredr(
  series_id = "T10Y2Y",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


# 10-Year Treasury Constant Maturity Minus 3-Month Treasury Constant Maturity  (T10Y3M)
yield_curve2 <- fredr(
  series_id = "T10Y3M",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


yield_curve3 <- yield_curve1 %>%
  dplyr::select(c("date", "value")) %>% 
  left_join(dplyr::select(yield_curve2, c('date', 'value')), by = 'date') %>%
  purrr::set_names(c("date",
                     "Yield-Curve-Two", "Yield-Curve-three")) %>% 
  dplyr::rename_all(~str_to_title(.))


yield_curve4 <- tbl_xts(yield_curve3)


highchart(type = "stock") %>% 
  hc_add_series(yield_curve4$`Yield-Curve-Two`, type = "line",
                name = 'two-year yield curve',
                color = "#d35400",
                lineWidth = 4.5,
                tooltip = list(valueSuffix = 'k')) |>
    hc_add_series(yield_curve4$`Yield-Curve-Three`, type = "line",
                  name = 'Three month yeild curve',
                  color = "#39057F",
                  lineWidth = 4.5,
                  tooltip = list(valueSuffix = 'k')) |>

  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
             color = 'black',
             fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) %>% 
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_title(text = 'Yield Curves USA',
           align = 'center',
           style = list(fontWeight = 'bold')) |>
  hc_legend(
    enabled = TRUE, 
    align = "top",
    verticalAlign = "top",
    layout = "vertical",
    verticalAlign=  'top')


```


Row
------------
### Stock Market

```{r stock_market, echo=FALSE}
# Dow Jones Industrial Average  (DJIA)

stock_market1 <- fredr(
  series_id = "DJIA",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


# S&P 500  (SP500)
stock_market2 <- fredr(
  series_id = "SP500",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')



stock_market3 <- stock_market1 %>% 
  select(c('date', 'value')) %>%  
  left_join(select(stock_market2,c('date', 'value')), by = 'date') %>% 
  set_names(c('date', 'Dow-Jones', 'S&P500')) 



stock_market4 <- tbl_xts(stock_market3)


  highchart(type = "stock") %>% 
  hc_add_series(stock_market4$`Dow-Jones`, type = "line",
                name = 'Dow-Jones',
                color = "#d35400",
                lineWidth = 4.5,
                tooltip = list(valueSuffix = 'k')) |>
    hc_add_series(stock_market4$`S&P500`, type = "line",
                  name = 'S&P500',
                  color = "#111111",
                  lineWidth = 4.5,
                  tooltip = list(valueSuffix = 'k')) |>

  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
             color = 'black',
             fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) %>% 
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_title(text = 'Stock Markets USA',
           align = 'center',
           style = list(fontWeight = 'bold')) |>
  hc_legend(
    enabled = TRUE, 
    align = "top",
    verticalAlign = "top",
    layout = "vertical",
    verticalAlign=  'top')



```

Row
--------------------------------------------------------------------------------
### Industrial Production
```{r industrial_production}

industrial_product <- fredr(
  series_id = "INDPRO",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm',
  units = 'lin')


p1 <- industrial_product %>% 
  select(c('date', "value")) %>% 
  mutate(growth = (value/lag(value,12)-1)*100)

p1_xts <- tbl2xts::tbl_xts(p1)

highchart(type = "stock") %>% 
  hc_add_series(p1_xts$growth, type = "line",
                name = 'Industrial Production',
                color = "#d35400",
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '%')) |>
  
 
  hc_xAxis(dateTimeLabelFormats = list(year = '%Y'), type = "datetime") |>
  
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) |>
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "Growth Rate Industrial Production USA"
  ) |>                      
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
             color = 'black',
             fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_legend(enabled = TRUE)  |>
  # hc_legend(
  #   align = "top",
  #   verticalAlign = "top",
  #   layout = "horizantal") |>
  hc_tooltip(shared = FALSE) |>
  hc_title(
    text = "<b>Industrial Prodution Growth rate</b>",
    margin = 20,
    align = "left",
    style = list(color = "black", useHTML = TRUE)
  )


```


### Consumer Sentiment 
```{r sentiment}
cons_sentiment <- fredr(
  series_id = "UMCSENT",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm',
  units = 'lin')



p1 <- cons_sentiment %>% 
  select(c('date', "value")) 

p1_xts <- tbl2xts::tbl_xts(p1)

highchart(type = "stock") %>% 
  hc_add_series(p1_xts$value, type = "line",
                name = 'Consumer Sentiment',
                color = "#0D1377",
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '%')) |>
  
 
  hc_xAxis(dateTimeLabelFormats = list(year = '%Y'), type = "datetime") |>
  
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) |>
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "Consumer Sentiment"
  ) |>                      
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
             color = 'black',
             fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_legend(enabled = TRUE)  |>
  # hc_legend(
  #   align = "top",
  #   verticalAlign = "top",
  #   layout = "horizantal") |>
  hc_tooltip(shared = FALSE) |>
  hc_title(
    text = "<b>Consumer Sentiment</b>",
    margin = 20,
    align = "left",
    style = list(color = "black", useHTML = TRUE)
  )

```

Row
-----------
### Housing Market
```{r housing_sector}
# New Privately-Owned Housing Units Authorized in Permit-Issuing Places: 
# Total Units  (PERMIT)
house_starts <- fredr(
  series_id = "PERMIT",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


# New Privately-Owned Housing Units Started: Total Units  (HOUST)
house_starts1 <- fredr(
  series_id = "HOUST",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


p_house <- house_starts %>% 
  select(c('date', "value")) |>
  left_join(dplyr::select(house_starts1, c('date', "value")), by = 'date') |>
  set_names(c("Date", "House-Permits", 'House-Starts')) 



p_house1 <-  tbl2xts::tbl_xts(p_house)



highchart(type = "stock") %>% 
  hc_add_series(p_house1$`House-Permits`, type = "line",
                name = 'Housing permits',
                color = "#d35400",
                lineWidth = 4.5,
                tooltip = list(valueSuffix = 'k')) |>
  hc_add_series(p_house1$`House-Starts`, type = "line",
                name = 'Housing starts',
                color = "#485CC7",
                lineWidth = 4.5,
                tooltip = list(valueSuffix = 'k')) |>
  
 
  hc_xAxis(dateTimeLabelFormats = list(year = '%Y'), type = "datetime") |>
  
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) |>
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "Housing Market"
  ) |>                      
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
             color = 'black',
             fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_legend(enabled = TRUE)  |>
  # hc_legend(
  #   align = "top",
  #   verticalAlign = "top",
  #   layout = "horizantal") |>
  hc_tooltip(shared = FALSE) |>
  hc_title(
    text = "<b>Housing Market Developments</b>",
    margin = 20,
    align = "left",
    style = list(color = "black", useHTML = TRUE)
  )


```


## Row

### Backing Ratio
```{r backing_ratio}

path <- "data/MFS_data.xlsx" 



dfs_nyf <- path %>% 
  excel_sheets() %>% 
  purrr::set_names() %>% 
  purrr::map(read_excel, path = path)

# 
# names(dfs_nyf)
# 
# dfs_nyf %>%  pluck('backing_ratio') %>% 
#   filter(entity_id == 'ECCU309') %>% 
#   mutate(date_dt = ymd(date_dt)) %>% 
#   mutate(rolling_std = rollapply(reporting_amount,width=3,
#                                  FUN=sd,fill=0,align="r")) %>% 
#   select(c(4,3,7)) %>% 
#   ggplot(aes(x = date_dt, y = rolling_std)) +
#   geom_line(linewidth = 1.3, lineend = 'round')

# p_backing <- 
p_backing <- dfs_nyf %>%  pluck('backing_ratio') %>% 
  filter(entity_id == 'ECCU309') %>% 
  mutate(date_dt = ymd(date_dt)) %>% 
  select(c(4,3)) %>% 
  dplyr::rename(date = date_dt)



p_backing1 <-  tbl2xts::tbl_xts(p_backing)



highchart(type = "stock") %>% 
  hc_add_series(p_backing1$reporting_amount, type = "line",
                name = 'Backing Ratio',
                color = "#0713CC",
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '%')) |>
 
  hc_xAxis(dateTimeLabelFormats = list(year = '%Y'), type = "datetime") |>
  
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) |>
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "Backing Ratio"
  ) |>                      
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
             color = 'black',
             fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_legend(enabled = TRUE)  |>
  # hc_legend(
  #   align = "top",
  #   verticalAlign = "top",
  #   layout = "horizantal") |>
  hc_tooltip(shared = FALSE) |>
  hc_title(
    text = "<b>ECCB Backing Ratio</b>",
    margin = 20,
    align = "left",
    style = list(color = "black", useHTML = TRUE)
  )

```



### Change Backing Ratio

```{r}

p_backing2 <- dfs_nyf %>%  
  pluck('backing_ratio') %>% 
  filter(entity_id == 'ECCU309') %>% 
  mutate(date_dt = ymd(date_dt)) %>% 
  select(c(4,3)) %>% 
  mutate(Change = round(reporting_amount - lag(reporting_amount,12) ),2) %>% 
  dplyr::rename(date = date_dt)



p_backing3 <-  tbl2xts::tbl_xts(p_backing2)



highchart(type = "stock") %>% 
  hc_add_series(p_backing3$Change, type = "line",
                name = 'Backing Ratio',
                color = "#33D105",
                lineWidth = 4.5,
                tooltip = list(valueSuffix = '%')) |>
 
  
 
  hc_xAxis(dateTimeLabelFormats = list(year = '%Y'), type = "datetime") |>
  
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) |>
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "Backing Ratio"
  ) |>                      
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
             color = 'black',
             fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_legend(enabled = TRUE)  |>
  # hc_legend(
  #   align = "top",
  #   verticalAlign = "top",
  #   layout = "horizantal") |>
  hc_tooltip(shared = FALSE) |>
  hc_title(
    text = "<b>Change In Backing Ratio (y-o-y)</b>",
    margin = 20,
    align = "left",
    style = list(color = "black", useHTML = TRUE)
  )
  
```

Row
-------------------------------------------------------------------------------
### Foreign Securities

```{r securities}


p_securities <- dfs_nyf %>%  pluck('securities') %>% 
  filter(entity_id == 'ECCU309') %>% 
  mutate(date_dt = ymd(date_dt)) %>% 
  select(c(4,3)) %>% 
  mutate(y = reporting_amount/1000000) %>% 
  dplyr::rename(date = date_dt)
  

p_securities1 <- tbl2xts::tbl_xts(p_securities)

highchart(type = "stock") %>% 
  hc_add_series(p_securities1$y, type = "line",
                name = 'Securities',
                color = "#F7C433",
                lineWidth = 4.5,
                tooltip = list(valueSuffix = 'B')) |>
 
  
 
  hc_xAxis(dateTimeLabelFormats = list(year = '%Y'), type = "datetime") |>
  
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) |>
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "Backing Ratio"
  ) |>                      
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
             color = 'black',
             fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_legend(enabled = TRUE)  |>
  # hc_legend(
  #   align = "top",
  #   verticalAlign = "top",
  #   layout = "horizantal") |>
  hc_tooltip(shared = FALSE) |>
  hc_title(
    text = "<b>Stock of Foreign Securities</b>",
    margin = 20,
    align = "left",
    style = list(color = "black", useHTML = TRUE)
  )  
  
 

```


### Foreign Assets

```{r foreign_assets}
p_fa <- dfs_nyf %>%  pluck('foreign_assets') %>% 
  filter(entity_id == 'ECCU309') %>% 
  mutate(date_dt = ymd(date_dt)) %>% 
  select(c(4,3)) %>% 
  dplyr::mutate( y = reporting_amount/1000000) %>% 
  dplyr::rename(date = date_dt)



p_fa1 <- tbl2xts::tbl_xts(p_fa)
  
highchart(type = "stock") %>% 
  hc_add_series(p_fa1$y, type = "line",
                name = 'Foreign-Assets',
                color = "#201802",
                lineWidth = 4.5,
                tooltip = list(valueSuffix = 'B')) |>
 
  
 
  hc_xAxis(dateTimeLabelFormats = list(year = '%Y'), type = "datetime") |>
  
  hc_rangeSelector(verticalAlign = "bottom",  
                   buttons = list(
                     list(type = 'all', text = 'All'),
                     list(type = 'ytd', text = 'YTD'),
                     list(type = 'month', count = 6, text = '6m'),
                     list(type = 'year', count = 1, text = '1y'),
                     list(type = 'year', count = 5, text = '5y'),
                     list(type = 'year', count = 10, text = '10y'))) |>
  hc_plotOptions(
    line = list(lineWidth = 4.5)) |>
  hc_exporting(
    enabled = TRUE, # always enabled
    filename = "Backing Ratio"
  ) |>                      
  hc_yAxis(labels = list(align = 'left',
                         style = list(
                           color = 'black',
                           fontSize = 'medium'))) %>% 
  hc_xAxis(lineColor ='black', lineWidth = 2,
           tickColor = 'black',
           labels = list(style = list(
             color = 'black',
             fontSize = 'medium')),
           dateTimeLabelFormats = list(year = "%Y"), 
           type = "datetime") %>% 
  hc_legend(enabled = TRUE)  |>
  # hc_legend(
  #   align = "top",
  #   verticalAlign = "top",
  #   layout = "horizantal") |>
  hc_tooltip(shared = FALSE) |>
  hc_title(
    text = "<b>Stock of Foreign Assets</b>",
    margin = 20,
    align = "left",
    style = list(color = "black", useHTML = TRUE)
  )    

```



## Row 

### Tourism Arrivals ECCU
```{r tourism, echo=FALSE}
path <- "data/realsector.xlsx"


df <- path %>%
  excel_sheets() %>% 
  purrr::set_names() %>% 
  map(read_excel, path = path)


df1 <- df[["TOTAL TOURSIM"]]


df2 <- df1 %>% select(c(6,7)) %>% 
  mutate(date_dt = as.Date(date_dt))


df_ts <- ts(df2[,2], start = c(2000,12), frequency = 12)



df_ts_sa <- decompose(df_ts, type = 'multiplicative')



df_ts_sa1 <- as_tibble(df_ts / df_ts_sa$seasonal)

df_tour <- cbind.data.frame(df2, df_ts_sa1) %>% 
  setNames(c('date', 'tourism', 'tourism_sa')) %>% 
  mutate(tourism_sa1= (tourism_sa /lag(tourism_sa,12))-1)


cap <- 'Data Source | ECCB\nData as at March 2023\nFigures are seasonally adjusted'
font <- 'Georgia'
df_tour %>% 
  filter(date >= as.Date('2016-01-01')) %>% 
  ggplot(aes(x= date, y = tourism_sa )) +
  geom_line(linewidth = 1.3) +
  scale_y_continuous(breaks = breaks_width(50000),
                     labels = label_comma()) +
  scale_x_date(date_breaks = '1 year',
               date_labels = '%Y',
               limits = c(as.Date('2016-01-01'),
                          as.Date('2023-06-01'))) +
  labs(caption = cap, y = 'Tourism Arrivals') +
  theme_minimal() +
  theme(axis.text = element_text(size = 15,color = 'black'),
        axis.title = element_text(size = 15,color = 'black'))

```

### Import Values ECCU



Row 
----------------------------------------------------------------

### Data table USA GDP
```{r}

gdp <- fredr(
  series_id = "GDPC1",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  units = 'cca')

gdp_cfnai <- fredr(
  series_id = "CFNAIMA3",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'q')

gdpnow <- fredr(
  series_id = "GDPNOW",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date())

gdp %>%  
  dplyr::select(c('date', 'value')) %>% 
  left_join(dplyr::select(gdp_cfnai,c('date', 'value')), by = 'date') |>
  left_join(dplyr::select(gdpnow,c('date', 'value')), by = 'date') |>
  setNames(c('date', 'GDP', 'CFNAI', 'GDP.Now')) %>% 
  mutate(across(where(is.numeric), ~round(.,2))) %>% 
  datatable(class = 'cell-border stripe',
          # colnames = toTitleCase(names()),
          extensions = 'Buttons', options = list(
            dom = 'Blfrtip',
            buttons = c('copy', 'csv', 'excel', 'pdf', 'print') )
)

```

Row 
----------------------------------------------------------------
### Data table Interest Rates 
```{r table1}

twoyear <- fredr(
  series_id = "DGS2",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


oneyear <- fredr(
  series_id = "DGS1",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')

threemonth <- fredr(
  series_id = "DGS3MO",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')

sixmonth <- fredr(
  series_id = "DGS6MO",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


tbills <- fredr(
  series_id = "TB3MS",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


fedfunds <- fredr(
  series_id = "FEDFUNDS",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


# 30-Year Fixed Rate Mortgage Average in the United States  (MORTGAGE30US)
mortg30 <- fredr(
  series_id = "MORTGAGE30US",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


# 15-Year Fixed Rate Mortgage Average in the United States  (MORTGAGE15US)
mortg15 <- fredr(
  series_id = "MORTGAGE15US",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')

# 10-Year Treasury Constant Maturity Minus 2-Year Treasury Constant Maturity  (T10Y2Y)
yield_curve1 <- fredr(
  series_id = "T10Y2Y",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


# 10-Year Treasury Constant Maturity Minus 3-Month Treasury Constant Maturity  (T10Y3M)
yield_curve2 <- fredr(
  series_id = "T10Y3M",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  frequency = 'm')


irates2 <- twoyear %>%
  dplyr::select(c("date", "value")) %>% 
  left_join(dplyr::select(oneyear, c("date", "value")), by = 'date') |>
  left_join(dplyr::select(sixmonth, c("date", "value")), by = 'date') |>
  left_join(dplyr::select(threemonth, c("date", "value")), by = 'date') |>
  left_join(dplyr::select(fedfunds, c("date", "value")), by = 'date') %>% 
  left_join(dplyr::select(mortg30, c('date', 'value')), by = 'date') %>% 
  left_join(dplyr::select(mortg15, c('date', 'value')), by = 'date') %>% 
  left_join(dplyr::select(yield_curve1, c('date', 'value')), by = 'date') %>%
  left_join(dplyr::select(yield_curve2, c('date', 'value')), by = 'date') %>%
  purrr::set_names(c("date","Two-year", "One-year", 'Six-months', 
                     "Three-months", 'Fed_Funds',"30-Year-Mortgage", "15-Year-Mortgage",
                     "Yield-Curve1", "Yield-Curve2")) %>% 
  dplyr::rename_all(~str_to_title(.))

irates2 %>%
  downloadthis::download_this(
    output_name = "Interest_rates",
    output_extension = ".csv",
    button_label = "Download data as csv",
    button_type = "success",
    has_icon = TRUE,
    icon = "fa fa-save"
  )

irates2 |>
  reactable(filterable = TRUE, 
            searchable = TRUE, 
            paginationType = "jump",
            defaultPageSize = 10,
            minRows = 20)
```


Row 
----------------------------------------------------------------
### Data table CPI
```{r}
cpi <- fredr(
  series_id = "CPIAUCSL",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  units = 'pc1')


cpi_core <- fredr(
  series_id = "CPILFESL",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  units = 'pc1')

# Inflation expectations data 1 year ahead only

inflation_exp <- fredr(
  series_id = "EXPINF1YR",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date())


pce <- fredr(
  series_id = "PCE",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  units = 'pc1')


pce_core <- fredr(
  series_id = "PCEPILFE",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date(),
  units = 'pc1')



# Trimmed Mean PCE Inflation Rate Dallas Fed
inflation_exp2 <- fredr(
  series_id = "PCETRIM12M159SFRBDAL",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date())


# 16% Trimmed-Mean Consumer Price Index Cleveland Fed
inflation_exp3 <- fredr(
  series_id = "TRMMEANCPIM159SFRBCLE",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date())


# Median Consumer Price Index
inflation_exp4 <- fredr(
  series_id = "MEDCPIM159SFRBCLE",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date())


inflation_exp1 <- fredr(
  series_id = "CORESTICKM159SFRBATL",
  observation_start = as.Date("1990-01-01"),
  observation_end = Sys.Date())

alt_inflation <- cpi %>% 
  dplyr::select(c('date', 'value')) %>% 
  left_join(dplyr::select(cpi_core,c('date', 'value')), by = 'date') |>
  left_join(dplyr::select(pce,c('date', 'value')), by = 'date') |>
  
  left_join(dplyr::select(pce_core,c('date', 'value')), by = 'date') |>
  left_join(dplyr::select(inflation_exp,c('date', 'value')), by = 'date') |>
  left_join(dplyr::select(inflation_exp2,c('date', 'value')), by = 'date') |>
  left_join(dplyr::select(inflation_exp3,c('date', 'value')), by = 'date') |>
  left_join(dplyr::select(inflation_exp4,c('date', 'value')), by = 'date')  |>
  left_join(dplyr::select(inflation_exp1,c('date', 'value')), by = 'date')  |>
  setNames(c('date', "CPI", "CPI-Core", "PCE", "PCE-Core", 
             'Trimmed-Mean-PCE', '16%-Trimmed-Mean-CPI', 
             'Median-CPI','Sticky.Price.inflation',
             'Inflation.Expectation')) %>% 
  mutate(across(where(is.numeric), ~round(.,2)))
             
# alt_inflation |>
#   reactable(filterable = TRUE, 
#             searchable = TRUE, 
#             paginationType = "jump",
#             defaultPageSize = 20,
#             minRows = 20)     


alt_inflation %>%
  downloadthis::download_this(
    output_name = "Inflation_rates",
    output_extension = ".csv",
    button_label = "Download data as csv",
    button_type = "success",
    has_icon = TRUE,
    icon = "fa fa-save"
  )


alt_inflation |>
  gt() |>
  opt_interactive(
    use_search = TRUE,
    use_filters = TRUE,
    use_resizers = TRUE,
    use_highlight = TRUE,
    use_compact_mode = TRUE,
    use_text_wrapping = FALSE,
    use_page_size_select = TRUE,
     page_size_default = 5) %>% 
   data_color(
    columns = CPI,
    palette = "Reds"
  ) |>
  data_color(
    columns = PCE,
    palette = "Greens"
  )

```

Row
-----------------
**For more information visits us at:**

- `r fa("globe", fill = "steelblue")` [ECCB](https://www.eccb-centralbank.org/)   
- `r fa("facebook", fill = "steelblue")` [ECCB](https://www.facebook.com/ECCBConnects/) 
-  `r fa("youtube", fill = "red")` [ECCB](https://www.youtube.com/channel/UCNRvzpgM5-GYe_z5z5lgX_Q)
- `r fa("linkedin", fill = "blue")` [ECCB](https://www.linkedin.com/in/eastern-caribbean-central-bank-137375147/)
- Maintained by:[email](allister.hodge@eccb-centralbank.org)  
- Contact: [RSDAD](RSDAD@eccb-centralbank.org)  

**Date Created:**`r format(Sys.Date(), '%b-%Y')`

```{r end}

library(beepr)
beep("fanfare")

```

